Interleaved Serial and Decision-Theoretic Planning for Practical Robot Control

### 2011-01-20 subarchitectures/planner.sa/trunk/src/latex/IJCAI/ijcai11.tex
clarification to englishizisationXX

\title{Interleaved Serial and Decision-Theoretic Planning for a Mobile Robot}
%%\title{Interleaved Serial and Decision-Theoretic Planning for
%%Practical Robot Control}

@@

From an automated planning perspective the problem of practical mobile
robot control in realistic environments poses many important and
contrary challenges.  On the one hand, the planning process must be
lightweight, robust, and timely. Over the lifetime of the robot it
must always respond quickly with new plans that accommodate exogenous
events, changing objectives, and the underlying unpredictability of
the environment.  On the other hand, in order to exhibit useful
behaviours the planning process must perform computationally expensive
reasoning about contingencies and possible revisions of subjective
beliefs according to quantitatively modelled uncertainty in acting and
sensing.
%%
Addressing these challenges, we develop a \emph{continual planning}
approach that {\em switches} between using a fast satisficing
``classical'' planner, to decide on the overall strategy, and
decision-theoretic planning to solve small subproblems where deeper
consideration of the sensing model is practical, and can significantly
impact overall performance. We demonstrate our approach in a realistic
robot exploration domain.

>>>>

%% \title{Interleaved Serial and Decision-Theoretic Planning for a Mobile Robot}

\title{Interleaved Serial and Decision-Theoretic Planning for
Practical Robot Control}

@@

From an automated planning perspective the problem of practical mobile
robot control in realistic environments poses many important and
contrary challenges.  On the one hand, the planning process must be
lightweight, robust, and timely. Over the lifetime of the robot it
must always respond quickly with new plans that accommodate exogenous
events, changing objectives, and the underlying unpredictability of
the environment.  On the other hand, in order to exhibit useful
behaviours the planning process must perform computationally expensive
reasoning about contingencies and possible revisions of subjective
beliefs according to quantitatively modelled uncertainty in acting and
sensing.
%%
Towards addressing these challenges, we develop a \emph{continual
planning} approach that {\em switches} between using a fast
satisficing ``classical'' planner, to decide on the overall strategy,
and decision-theoretic planning to solve small subproblems where
deeper consideration of the sensing model is both practical, and can
significantly impact overall performance. We demonstrate our approach
in large problems from a realistic robot exploration domain.
